Effects of Unemployment Benefits and Uncertainty in Heterogeneous Models

### 2017-01-23 presentation/presentation.tex
Final version.

	\item {
	These magnitude of these changes varies for different levels of risk aversion.
	}

		\item {
	How do these aggregates compare to a situation with perfect insurance? 
	}

@@

\begin{frame}{Distribution of capital}
	\begin{itemize}

	\item {
These processes are driven by changes in precautionary savings reacting to changes in different levels of idiosyncratic risk. 
	}
	\item {
Let us look at the different distributions of capital. 
	}

@@

\begin{figure}[!tbp]
  \centering
  \begin{minipage}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{distribution1}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{distribution2}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{distribution3}
  \end{minipage}
\end{figure}
\ \ \ \ \ \ \  rw = 0.01 \ \ \ \ \ \ \ \ \ \ \ \ rw = 0.42579 \ \ \ \ \ \ \ \ \ \ \ \ \ rw = 0.8
\end{frame}

\begin{frame}{Moments Employed}

\centering
\begin{tabular}{l*{6}{c}r}
UI             & Mean & Median & Std & Skewness\\
\hline
Low 			& 22.24 & 22.56 & 14.97 & 1.31\\
Medium         & 17.94 & 17.60 & 17.68 & 1.41\\
High          & 17.41 & 15.73 & 18.07 & 1.41 \\
\end{tabular}

\begin{frame}{Moments Unemployed}

\centering	
\begin{tabular}{l*{6}{c}r}
UI             & Mean & Median & Std & Skewness\\
\hline
Low 			& 20.35 & 20.60 & 16.08 & 1.39\\
Medium         & 16.88 & 16.56 & 18.45 & 1.41\\
High          & 17.17 & 15.51 & 18.23 & 1.41 \\
\end{tabular}

>>>>

	\item {
	The magnitude of impact varies for different levels of risk aversion.
	}

		\item {
	How do the different levels of the aggregates compare to a situation with perfect insurance? 
	}

@@

@@

\begin{figure}[!tbp]
  \centering
  \begin{minipage}[b]{0.325\textwidth}
    \includegraphics[width=\textwidth]{distribution1}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.325\textwidth}
    \includegraphics[width=\textwidth]{distribution2}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.325\textwidth}
    \includegraphics[width=\textwidth]{distribution3}
  \end{minipage}
\end{figure}
\ \ \ \ \ \ \  rw = 0.01 \ \ \ \ \ \ \ \ \ \ \ \ rw = 0.42579 \ \ \ \ \ \ \ \ \ \ \ \ \ rw = 0.8
\end{frame}
